% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Tyler Christiansen}}

480 Timberhead Ln\ \ \textbullet
\ \ Foster City, CA 94404
\\
(864) 346-4095\ \ \textbullet
\ \ mail@tylerc.me
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Production Networks, Aol}}
		{\textbf{San Mateo, CA}}
	\\
	\headerrow
		{\emph{Network Engineer}}
		{\emph{April 2014 -- Present}}
	\begin{itemize*}
        \item \emph{Hired} as the sole network engineer for Adap.tv.  Managed application delivery infrastructure, from services on servers to
            network switches, routers, firewalls, and load balancers.  Served as lead for all networking decisions, design, and trouble.
        \item \emph{Expanded} to Aol Production Networks team to design, support, and maintain the backbone and data center networks.
            \\
            \\
            Projects include: Adap.tv and Aol network merger, network automation design and build, AWS VPC design and integration, and
            application delivery infrastructure design
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Operations, Beats Music}}
		{\textbf{San Francisco, CA}}
	\\
	\headerrow
		{\emph{Network Engineer}}
		{\emph{June 2013 -- April 2014}}
	\begin{itemize*}
        \item \emph{Recruited} to design and support national data center networks for a large scale music streaming service.  Responsible for
            selecting and implementing network management and monitoring software.  Responsible for service status reporting.  Ensured 100\%
            network infrastructure availability.  Established IPSec+NAT for communication with third party partners.
        \\
        \\
        Projects include: hadoop network infrastructure design, load balancer acquisition, network monitoring infrastructure, partner communication
        encryption.
	\end{itemize*}
    
    \item
	\headerrow
		{\textbf{Core IP/MPLS, Windstream Communications}}
		{\textbf{Greenville, SC}}
	\\
	\headerrow
		{\emph{Network Engineer}}
		{\emph{April 2012 -- July 2013}}
	\begin{itemize*}
        \item \emph{Hired} to support national core IP/MPLS network.  Handled escalated L2/L3 VPNs and VPLS service.  Handled core MPLS and
            BGP issues.  Designed network maintenance events to proactively and reactively maintain the health of network services.
            Implemented network change controls to enable new core and edge services.
	\end{itemize*}

    \item
	\headerrow
		{\textbf{Network Operations, Windstream Communications}}
		{\textbf{Greenville, SC}}
	\\
	\headerrow
		{\emph{Network Analyst}}
		{\emph{April 2011 -- April 2012}}
	\begin{itemize*}
        \item \emph{Hired} to monitor national data, optical, and voice networks.  Served as technical lead for data network triage.
            Trained new hires in process and triage for voice, optical, and data network elements.  Ensured proper escalation and
            maintenance management.
	\end{itemize*}

    \item
	\headerrow
		{\textbf{Plant Operations, Windstream Communications}}
		{\textbf{Milledgeville, GA}}
	\\
	\headerrow
		{\emph{OSP Technician}}
		{\emph{March 2009 -- April 2011}}
	\begin{itemize*}
        \item \emph{Hired} to install and support outside plant.  Installed analog voice and xDSL services for residential and
            business customers.  Served as technical lead for xDSL and small business networking services for area.
	\end{itemize*}


\end{itemize}

% This makes for a good place to force a pagebreak depending on your content and page flow.
%\pagebreak

\hrule
\vspace{-0.4em}
\subsection*{Core Technical Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
    \item[Specialties:]
        Network automation and change control using Git, Gerrit, Jenkins, Ansible, and Python.
    \item[Programming Languages:] 
        Bash, Python, Ruby
\end{description*}
\end{indentsection}


\hrule
\vspace{-0.4em}
\subsection*{Talks Given}

\begin{itemize}
    \parskip=0.1em

    \item
    \headerrow
        {\textbf{SF Network Automation Meetup}}
        {\textbf{July 2014}}
    \\
    \headerrow
        {\emph{Continuous Deployment with Ansible}}
        {\emph{Introduction to using Ansible to kickstart automated network changes.}}

\end{itemize}

\end{document}
